\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Vamshi Pasunuru\vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
CSA Department,             & {\it Mobile:}  (091) 8105186170 \\            
Indian Institute of Science & {\it E-mail (Work):}  vamshi@dsl.serc.iisc.ernet.in\\       
Bangalore, 560012, India.  & {\it WWW: http://pvam.github.io} \\     
\end{tabular}


\section{\sc Research Interests}

Database Systems (Query Optimization, Data Analytics), Algorithms.

\section{\sc Education}
{\bf Indian Institute of Science (IISc)}, Bangalore, Karnataka, India\\
{\em Department of Computer Science and Automation (CSA)} 
%\vspace*{-.1in}
\begin{list1}
\item[]  M.E , July 2014-16 (expected)
\begin{list2}
\vspace*{.05in}
%\item Dissertation Topic:  ``Nonstationary Covariance Models for
%  Spatial Data and Regression Problems'' 
%%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
%
\item Focus : Database Systems
\item Advisor:  Prof. Jayant R. Haritsa
\end{list2}
\end{list1}

{\bf Osmania University}, Hyderabad, Telangana, India.\\
%{\em Department of Mathematics and Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] B.E, Computer Science and Engineering ,  June, 2014
\end{list1}
\section{\sc Experience}

Technical student community, {\bf Microsoft, India} - June 2011-12.\\
%Intern, {\bf Startup village, BlackBerry} - Summer 2013. \\
Teaching Assistant,  {\bf Database Management System, CSA, IISc} - Aug-Dec 2015
\section{\sc Selected Projects}
{\bf Predicting Query Execution Time}
\hfill {\bf June 2015  - }\\
Query optimizer's cost model is insufficient for accurately predicting execution time. The goal is to come up with relevant metrics to capture CPU and I/O time for different query operators with a trade-off between accuracy and running time. 

{\bf Finding similarity across relations using Support estimation}
\hfill {\bf January-May 2015}\\
Developed a sampling based estimation algorithm to find the similarity across relations. Goal is to find the similarity by looking at a fraction of data at both source as well as target and come up with relevant attributes to estimate similarity. 

{\bf Enhancing NECTAR}
\hfill {\bf  January-May 2015}\\
NECTAR(Nash Equilibria CompuTAtion Resource) is a software tool for computing Nash equilibria of strategic form games and extensive form games. As part of the project, we integrated an open source linear programming solver "lpsolve" into the package and also made it web-accessible.

{\bf Analytics on Encrypted Database}
\hfill {\bf  August-December 2014}\\
Developed techniques to perform Nearest neighbour queries on 2-Dimensional encrypted data. The solution deals with partitioning encrypted  data into Voronoi cells to have minimal data transfer over network. We have also proposed an extension to deal with higher dimensional data.

{\bf Wordtrix}
\hfill {\bf  [B.E project] August 2013-June 2014}\\
Built an on-line multi-player game based on Boggle (An old word puzzle). As part of this, we developed algorithms to generate games which have sufficient score, protocols to ensure accurate timing and to maintain the user's progress. 

{\bf Free SMS}
\hfill {\bf  [Hobby project] August 2011-December 2013}\\
Built a mobile app which aggregates several free on-line SMS portals each having certain restrictions. As the Services are unreliable, app automatically picks the best service among all feasible services. Got \textbf{1 Million} downloads in windows phone store alone!

\section{\sc Others} 
\begin{list2}
\item Secured All India Rank- 86 in Graduate Aptitude Test in Engineering (GATE)- 2014.
%programming competitions.
\item Google APAC 2016  University Graduates Test Round C: 209/1416.
\item Microsoft Imagine Cup 2012 Software Design (India) Top 33 Team. 
\item Won multiple hackathons including Intel innovation challenge at IIIT Hyderabad and Windows 8 camp 2012 at Bangalore.
\item Semi-active competitive programmer. Topcoder : Rating 1294, Country rank 110/2300. \\Handle : \textbf{vamshipasunuru}
\item Developed a ML model with 96\% accuracy at IISc open days 2013 twitminer (an online machine learning programming contest). 
\item Morgan Stanley Codeathon 2015, Rank: 168/ 4153.
\item World Cup Semifinals - University Level CodeSprint, Rank:  280/ 1411.
%\item Teaching Assistant in CSA, IISc for E0261: Database Management System Course offered by Prof. Jayant Haritsa for Aug 2015 - till date.

\end{list2}
\section{\sc References}
\begin{enumerate}
\item Prof. Jayant R. Haritsa , Chair, CSA Dept, IISc. (haritsa@dsl.serc.iisc.ernet.in) 
\item Prasad M Deshpande, STSM and Manager, IBM Research,  Bangalore.(prasadmd0@gmail.com)
\end{enumerate}

\section{\sc Declaration}
I hereby declare that all the details furnished above are true to the best of my knowledge and belief. 
\begin{flushright}
VAMSHI
\end{flushright}

\end{resume}
\end{document}




